---
title: "Part 1 - stringr functions"
author: "Roshni Katrak-Adefowora"
date: "2/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


### Detect string patterns with `str_detect()`

```{r}
#create vector with number of different strings
vec <- c(" A Unicorn   Fish ", "add   cornmeal", "French FRIES", "acorn Squash " )

#which string has "corn"?
str_detect(vec, pattern = "corn")
```

Use `str_detect()` with filter to keep rows that are TRUE
```{r}
walk_sub <- starwars %>% 
  filter(str_detect(name, pattern = "walk"))

walk_sub

#can use str_subset()
```

### Replace a string pattern with something else

Use `str_replace()` to replace existing strong pattern with something else
```{r}
vec_bren <- str_replace(vec, pattern = "corn", replacement = "COOL")

vec_bren
```

replace the pattern "Sky" with the pattern "TORNADO"
```{r}
sw_tornado <- starwars %>% 
  mutate(name = str_replace(name, pattern = "Sky", replacement = "TORNADO"))
```

### Use `str_trim()` to remove excess leading and trailing whitespace

### Use `str_squish` to remove excess leading, trailing, and interior whitespace

```{r}
str_trim(vec)

str_squish(vec)
```

### Use `str_to_*()` to convert case

```{r}
str_to_lower(vec) #more coder friendly, and gets everything in same case so that we don't have mismatching outcomes because of different case (ex: corn vs Corn)
str_to_upper(vec)
str_to_title(vec)
```

### Using these in combination

```{r}
sw_combo <- starwars %>% 
  filter(str_detect(name, pattern = "Darth")) %>% 
  mutate(name = str_replace(name, pattern = "Darth", replacement = "LLAMA")) %>% 
  mutate(name = str_to_lower(name))
```

